\section{\scshape State of art}\label{sec:state-of-art}

\subsection{Related work}
\begin{frame}{Related work}
	\begin{itemize}
		\item Machine Learning
		\begin{itemize}
			\item Support Vector Machines
			\item Neural networks
			\item Hidden Markov Models
			\item Gaussian Mixture of Models
		\end{itemize}
		\item Computer Vision, 3D perception and Human Machine Interface
		\begin{itemize}
			\item Visual, geometric feature association
			\item Template, shape matching
			\item Color, intensity, texture segmentation
			\item Human-robot cooperation
		\end{itemize}
		\item Augmented Reality
		\begin{itemize}
			\item Projection mapping with DLP and laser projectors
		\end{itemize}
		\item Natural Language Processing
		\begin{itemize}
			\item N-gram models
		\end{itemize}
	\end{itemize}
\end{frame}

\subsection{Related work (hardware)}
\begin{frame}{Related work (hardware)}
	\begin{itemize}
		\item Robot manipulators
		\begin{itemize}
			\item Robotic arms
			\item Motion planners
			\item Robotic grippers
			\item Force control assembly
			\item Automatic tool change
			\item Environment fixtures
		\end{itemize}
		\item Perception sensors
		\begin{itemize}
			\item Image
			\item Stereo vision
			\item Camera-laser
			\item Structured light methods
			\item Time of Flight methods
		\end{itemize}
	\end{itemize}
\end{frame}

\subsection{Related work (software)}
\begin{frame}{Related work (software)}
	\begin{itemize}
		\item Frameworks
		\begin{itemize}
			\item Robot Operating System (ROS)
			\item Rapyuta
			\item OpenEASE
			\item CTAM
			\item RoboBrain
			\item KnowRob
		\end{itemize}
		\item Libraries
		\begin{itemize}
			\item Point Cloud Library (PCL)
			\item Open Computer Vision (OpenCV)
			\item Gazebo simulator
		\end{itemize}
	\end{itemize}
\end{frame}

\subsection{Main related research publications}
\begin{frame}{Main related research publications}
	\begin{itemize}
		\item Assembly operations
		\begin{itemize}
			\begingroup
			\scriptsize
			\item U. Thomas and F. M. Wahl, "A system for automatic planning, evaluation and execution of assembly sequences for industrial robots," Intelligent Robots and Systems, 2001. Proceedings. 2001 IEEE/RSJ International Conference on, Maui, HI, 2001, pp. 1458-1464 vol.3. \textbf{(seminal paper)}
			\item U. Thomas, F. M. Wahl, J. Maass and J. Hesselbach, "Towards a new concept of robot programming in high speed assembly applications," 2005 IEEE/RSJ International Conference on Intelligent Robots and Systems, 2005, pp. 3827-3833.
			\item U. Thomas, B. Finkemeyer, T. Kroger and F. M. Wahl, "Error-tolerant execution of complex robot tasks based on skill primitives," Robotics and Automation, 2003. Proceedings. ICRA '03. IEEE International Conference on, 2003, pp. 3069-3075 vol.3.
			\item U. Thomas, M. Barrenscheen and F. M. Wahl, "Efficient assembly sequence planning using stereographical projections of C-space obstacles," Assembly and Task Planning, 2003. Proceedings of the IEEE International Symposium on, 2003, pp. 96-102.
			\item D. Surdilovic, G. Schreck and U. Schmidt, "Development of Collaborative Robots (COBOTS) for Flexible Human-Integrated Assembly Automation," Robotics (ISR), 2010 41st International Symposium on and 2010 6th German Conference on Robotics (ROBOTIK), Munich, Germany, 2010, pp. 1-8.
			\endgroup
		\end{itemize}
	\end{itemize}
\end{frame}

%\subsection{Main related research publications}
\begin{frame}{}
	\begin{itemize}
		\item Robot arm control and path planning
		\begin{itemize}
			\begingroup
			\scriptsize
			\item C. Liu and M. Tomizuka, "Modeling and controller design of cooperative robots in workspace sharing human-robot assembly teams," 2014 IEEE/RSJ International Conference on Intelligent Robots and Systems, Chicago, IL, 2014, pp. 1386-1391.
			\item J. S. You, D. H. Kim, S. J. Lim, S. P. Kang, J. Y. Lee and C. S. Han, "Development of manipulation planning algorithm for a dual-arm robot assembly task," 2012 IEEE International Conference on Automation Science and Engineering (CASE), Seoul, 2012, pp. 1061-1066.
			\item U. Thomas and F. M. Wahl, "A system for automatic planning, evaluation and execution of assembly sequences for industrial robots," Intelligent Robots and Systems, 2001. Proceedings. 2001 IEEE/RSJ International Conference on, Maui, HI, 2001, pp. 1458-1464 vol.3.
			\endgroup
		\end{itemize}
		
		\item Human Machine Interface
		\begin{itemize}
			\begingroup
			\scriptsize
			\item A. Roitberg, A. Perzylo, N. Somani, M. Giuliani, M. Rickert and A. Knoll, "Human activity recognition in the context of industrial human-robot interaction," Signal and Information Processing Association Annual Summit and Conference (APSIPA), 2014 Asia-Pacific, Siem Reap, 2014, pp. 1-10.
			\endgroup
		\end{itemize}
	\end{itemize}
\end{frame}

\subsection{Main conferences and journals}
\begin{frame}{Main conferences and journals}
	\begin{itemize}
		\item Conferences
		\begin{itemize}
			\item ICRA - IEEE International Conference on Robotics and Automation
			\item IROS - IEEE/RSJ International Conference on Intelligent Robots and Systems
			\item ICCV - IEEE International Conference on Computer Vision
		\end{itemize}
		\item Journals
		\begin{itemize}
			\item International Journal of Robotics Research (SJR - 4.184)
			\item IEEE Transactions on Industrial Informatics (SJR - 2.973)
			\item IEEE Transactions on Robotics (SJR - 2.884)
			\item IEEE Robotics and Automation Magazine (SJR - 1.832)
			\item Robotics and Computer-Integrated Manufacturing (SJR - 1.621)
			\item Robotics and Autonomous Systems (SJR - 1.377)
		\end{itemize}
	\end{itemize}

\end{frame}

\subsection{Related research projects}
\begin{frame}{Related research projects}
	\begin{itemize}
		\item Saphari
		\begin{itemize}
			\item Safe and Autonomous Physical Human-Aware Robot Interaction
		\end{itemize}
		\item Rosetta
		\begin{itemize}
			\item RObot control for Skilled ExecuTion of Tasks in natural interaction with humans; based on Autonomy, cumulative knowledge and learning
		\end{itemize}
		\item JAHIR
		\begin{itemize}
			\item Joint-Action for Humans and Industrial Robots
		\end{itemize}
		\item Charm
		\begin{itemize}
			\item Collaborative, Human-focused, Assistive Robotics for Manufacturing
		\end{itemize}
		\item RoboEarth
		\item KnowRob
	\end{itemize}
\end{frame}

\subsection{Related research groups}
\begin{frame}{Related research groups}
	\begin{itemize}
		\item Aalborg Universitet
		\item DLR - Deutsches Zentrum für Luft- und Raumfahrt
		\item ETH Zurich
		\item fortiss
		\item Fraunhofer Institute for Manufacturing Engineering and Automation
		\item Lunds Universitet
		\item Technische Universität Chemnitz
		\item Technische Universität München
		\item TU/e
		\item Universität Bremen
	\end{itemize}
\end{frame}

%\subsection{Related research groups}
%\begin{frame}{Related research groups}
%	Text.
%\end{frame}
